Infinite Diameter Confidence Sets in Hedges' Publication Bias Model

### 2020-08-06 infiniteci.tex
:+1: Small changes to contour plot.

\documentclass[twoside]{article}
\usepackage{arxiv}

%%% ============================================================================
%%% Macros.
%%% ============================================================================
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\argmin}{argmin}
\DeclareMathOperator{\Cor}{Cor}
\DeclareMathOperator{\Cov}{Cov}
\DeclareMathOperator{\diag}{diag} 
\DeclareMathOperator{\argmax}{argmax}

\title{Infinite diameter confidence sets in the selection function model for publication bias}

\author{
  Jonas Moss \orcid{0000-0002-6876-6964} \\
  Department of Mathematics, University of Oslo\\
  PB 1053, Blindern, NO-0316, Oslo, Norway \\
  \it{jonasmgj@math.uio.no}
}

@@

\begin{document}
\maketitle
\begin{abstract}
Meta-analysis is the quantitative combination of results from different studies. The assumptions of classical meta-analysis models are not satisfied whenever publication bias is present, which causes inconsistent parameter estimates. A popular method to account for publication bias in meta-analysis is the selection function model, but frequentist estimation of this model is problematic. This paper shows there is no confidence set of guaranteed finite diameter for the mean and heterogeneity parameters in the selection function model. The proof is based on a generalization of the Gleser--Hwang theorem.
\end{abstract}

\keywords{meta-analysis \and publication bias \and selection function model \and p-hacking}

@@

Meta-analysis is the quantitative combination of results from different studies with the goal of reducing sampling error \citep{lipsey2001practical}.
Publication bias occurs when the published research literature is
not representative of the all the research that has actually been
done \citep{rothstein2006publication}. An important case of publication
bias is when publication decisions are made based on \textit{p}-values
\citep{sterling1959publication}, which, along its sister phenomenon \textit{p}-hacking \citep{simmons2011false},
can cause seriously biased conclusions when not accounted
for \citep{simmons2011false,moss2019modelling}.

One of the most important models for meta-analysis is the normal random effects
model with normal likelihoods where the
standard deviations are assumed to be known \citep{hedges1998fixed}.
The likelihood for an observation in this model is $\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})$,
where $\phi(x\mid\mu,\sigma)$ is the normal density with
mean $\mu$ and standard deviation $\sigma$. The parameter $\tau$ is the standard deviation of the random effects distribution, known as the heterogeneity parameter. The $\sigma_i$s are the study-specific standard errors, and $\theta_0$ is the mean of the effect size distribution. A modification of the random effects meta-analysis model due to \citet{hedges1984estimation}
allows us to account for \textit{p}-value based publication bias.

Let $u=\Phi(-x_{i}/\sigma_{i})$ be the standard one-sided
\textit{p}-value for the null hypothesis $\theta_{i}=0$, and $w(u)$
a probability for each $u$. The selection function meta-analysis
model \citep{hedges1984estimation,hedges1992modeling} based on
the\emph{ p}-value $u$ is
\begin{equation}
f(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})\propto\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})w(u)\label{eq:Publication bias model}
\end{equation}
The model is also known as the weighting function publication bias
model. Here is an interpretation of it:
\begin{quote}
Alice is an editor who receives a study with \textit{p}-value $u$.
Her publication decision is a random function of this \textit{p}-value. That is, 
she will publish the study with some probability $w(u)$.
Every study you will ever read in Alice's journal has survived this
selection mechanism, the rest are lost forever.
\end{quote}
This is a rejection sampling \citep{von1951various,flury1990acceptance}
procedure. The publication probability function is likely to be well
approximated by a step function, with cutoffs such as $0.01,0.025$
and $0.05$ being especially important. To model this, let $\alpha$
be a vector with $0=\alpha_{0}<\alpha_{1}<\cdots<\alpha_{J}=1$ and
$\rho$ be a non-negative vector in $[0,1]^{J}$ with $\rho_{1}=1$.
Now define $w(u\mid\rho,\alpha)=\sum_{j=1}^{J}\rho_{j}1_{(\alpha_{j-1},\alpha_{j}]}(u)$.
This is a step function where the value of $w$ on each step $(\alpha_{j-1},\alpha_{j}]$
is the probability of acceptance for a study with a\emph{ p}-value
$u$ falling inside the interval $(\alpha_{j-1},\alpha_{j}]$. I will
call the density proportional to $\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})w(u;\rho,\alpha)$
the step function publication bias model and denote it $f(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})$.

The step function publication bias model was first used by \citet{hedges1984estimation},
who used an $F$ distribution instead of a the normal distribution
and a single step in $w(u\mid\rho,\alpha)$. \citet{iyengar1988selection}
studied other choices of $w$ while \citet{citkowicz2017parsimonious}
used a beta density publication probability function instead of a
step function. \citet{hedges1992modeling} is an accessible paper
about the model.

Frequentist estimation of the step function publication bias model
is problematic, as noted by \citet[Appendix, 1]{mcshane2016adjusting}.
The purpose of this paper is to formalize and prove exactly how bad frequentist estimation of this model can be. I do this by proving there are no confidence sets of guaranteed finite diameter for the mean parameter $\theta_{0}$
and the heterogeneity parameter $\tau$ for any coverage $1-\alpha$.
This is a problematic result for two reasons: (i) It would be hopeless
to report confidence sets for $\tau^{2}$ like $[0.5,\infty)$,
as they have no practical value. (ii) It shows that the automatic confidence
sets procedures that are guaranteed to yield finite confidence sets
of some positive nominal coverage, such as bootstrapped confidence
sets, likelihood-ratio based confidence sets, and subsampling confidence
sets never have true coverage greater than $0$ \citep[see][]{gleser996bootstrap}.

The main result of this paper is the following theorem.
\begin{thm}
\label{prop:p-hacking infinite confidence interval}Let $h(x)=\prod_{i=1}^{n}f(x_{i}\mid\theta_{0},\tau,\sigma_{i})$
be the density of a $n$ independent observations from a step function
publication bias model. Then $h$ has no almost surely finite diameter
confidence set for $\left|\theta\right|$ or $\sigma$ of non-zero
coverage.
\end{thm}

\section{Definitions and Proofs}
Let $P_{\theta},\theta\in\Theta$ be a family of dominated probability
measures with densities $p_{\theta}$. Let $g:\Theta\to E$ for some
set $E$ equipped with a positive function $\left\Vert \cdot\right\Vert :E\to[0,\infty)$.
Here $g$ maps $\theta$ to the parameter we wish to form a confidence
set for, sometimes called a \textit{focus parameter} ((cite Nils)). For instance, $g(\theta) = \theta$ or $g(\theta) = E_\theta(X)$, the expectation of some random variable $X$ calculated under $P_\theta$.

The function $\left\Vert \cdot\right\Vert$ measures the \textit{size} of each $e \in E$. It could be a norm if $E$ is a vector space, and below it is the
absolute value $\left|\cdot\right|$.

A random set $C$ is a confidence set for $g(\theta)$ with coverage probability $1-\alpha$
if $P_{\theta}(g(\theta)\in C)\geq1-\alpha$
for all $\theta$. An\emph{ }acceptance set with level $\alpha$ has
the property than $P_{\theta}(A_{g(\theta)})\geq1-\alpha$.
There is a well known duality between confidence sets and acceptance
sets: For each confidence set $C$ there is a collection of acceptance
sets $A_{g(\theta)}$ satisfying $\omega\in A_{g(\theta)}$ if and only if $g(\theta)\in C(\omega)$. The classical reference for these concepts is of \citet[chapter 3.5]{lehmann2006testing}

We will need terminology for the diameter of the confidence set according
to the function $\left\Vert \cdot\right\Vert $. The diameter is
a random variable, $D=\textrm{sup}_{\eta\in C}\left\Vert \eta\right\Vert $.
A confidence set has infinite diameter at $\theta$ with positive
probability if $P_{\theta}(D=\infty)>0$. If $P_{\theta}(D=\infty)>0$
for all $\theta$, we will say that $D$ has infinite diameter with
positive probability.

The main ingredient in the proof of Theorem \ref{prop:p-hacking infinite confidence interval}
is Theorem \ref{thm:Infinite diameter main theorem}, an extension
and reformulation of the Gleser--Hwang theorem \citep{gleser1987nonexistence}. 
They used their theorem o prove the non-existence of confidence sets with
guaranteed finite diameter for models such as the errors-in-variables
regression model ((cite)) and Fieller's ratio of means problem ((cite)). \citet[theorem 1]{berger1999integrated}
is a similar extension of the Gleser--Hwang theorem.

The problem with non-existence
of confidence sets with guaranteed finite diameter for finite-dimensional
parameters has not received much attention in the statistical literature,
as lamented by \citet{gleser996bootstrap}. Some references in this
area are \citet{bahadur1956nonexistence}, who studied infinitely
large confidence sets in non-parametric estimation of the mean, \citeauthor{romano2004non}'s
(2004) extension of their results, \citet{Donoho1988-hg} and \citet{Pfanzagl1998-fe}.
\begin{lem}
Let $C$ be a confidence set and $A_{g(\theta)}$ its associated
acceptance sets. If there exists a sequence $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$
with $\left\Vert g(\theta_{n})\right\Vert \to\infty$ such
that $\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0,$then
the diameter of $C$ at $\theta$ is infinite with positive probability.
\end{lem}
\begin{proof}
Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$
for each $n$; such a sequence can always be found by appropriately
filtering the original $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$.
Since $\left\{ D\geq n\right\} $ is a decreasing sequence of sets,
$P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)$
for each $\theta$. From $A_{g(\theta_{n})}\subseteq\left\{ D\geq n\right\} $
it follows that $P_{\theta}(A_{g(\theta_{n})})\leq P_{\theta}(D\geq n)$,
thus $P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)\geq\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0$.
\end{proof}
This is the extension of the Gleser--Hwang theorem.
\begin{thm}
\label{thm:Infinite diameter main theorem}If there exists a sequence
$\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$ with $\left\Vert g(\theta_{i})\right\Vert \to\infty$
such that $p_{\theta_{i}}\to f^{\star}$ pointwise and $\textrm{supp}p_{\theta}=\textrm{supp}f^{\star}$
for each $\theta$, then every confidence set with coverage $1-\alpha>0$
has infinite diameter with positive probability.
\end{thm}
\begin{proof}
Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$.
By a variant of the dominated convergence theorem \citep[Exercise 16.4a]{billingsley1995probability}, $\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
Since $A_{g(\theta_{n})}\subseteq\left\{ D\leq n\right\}$, we have 
$1-\alpha\leq\int_{A_{g(\theta_{n})}}p_{\theta_{n}}d\mu\leq\int_{D\geq n}p_{\theta_{n}}d\mu$
for all $n$, thus $\int_{D=\infty}f^{\star}d\mu>1-\alpha>0$. The
result follows from $P_{\theta}(D\geq n)=\int_{D\geq n}(p_{\theta}/p_{\theta_{n}})p_{\theta_{n}}d\mu>\int_{D=\infty}(p_{\theta}/f^{\star})f^{\star}d\mu>0$.
\end{proof}
This is an extension of Theorem \ref{thm:Infinite diameter main theorem}
to mixture distributions.
\begin{prop}
\label{cor:Mixture model corollary}Let $f_{\theta}^{1},f_{\theta}^{2},\ldots$
be a finite or infinite sequence of densities, $\pi(\theta)$
a countable probability vector and $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
a mixture distribution. Assume there is a sequence $\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$
with $\left\Vert g(\theta_{i})\right\Vert \to\infty$ such
that $f_{\theta_{i}}^{1}\to f^{\star}$ pointwise and $\textrm{supp}f_{\theta}^{1} = \textrm{supp}f^{\star}$
for each $\theta$ . If there is a parameter $\theta'\in\Theta$ satisfying
$\pi_{1}(\theta')>\alpha$, the mixture $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
admits no almost surely finite diameter confidence set of coverage
$1-\alpha$ for $g(\theta)$.
\end{prop}

\begin{proof}
Let $C$ be confidence set for $g(\theta)$ with coverage
$1-\alpha$. Since $\pi_{1}(\theta')>\alpha$ by assumption,
$C$ must include a confidence $C_{1}$ for $f_{\theta}^{1}$ of some
positive coverage. But by Theorem \ref{thm:Infinite diameter main theorem},
$C_{1}$ has infinite diameter with positive probability for all $\theta$.
Since $C\supseteq C_{1}$, $C$ has infinite diameter with positive
probability too.
\end{proof}
The following lemma is a proof of proposition \ref{prop:p-hacking infinite confidence interval}
for the special case when no non-significant studies are published.
Let $\phi_{[a,b)}(x\mid\theta,\sigma)$ denote
the density of a normal variable with mean $\theta$ and standard
deviation $\sigma$ truncated to $[a,b)$.
\begin{lem}
\label{lem:One-sided normal limit}Let $f$ be a normal density truncated
to $[c,\infty)$ with underlying mean $\theta_{n}=-n-c$
and standard deviation $\sigma_{n}=n^{1/2}$. Then $\phi_{[c,\infty)}(x\mid\theta_{n},\sigma_{n})$
converges pointwise to $\exp(-x-c)$, the density of a
shifted exponential.
\end{lem}

\begin{proof}
The formula for $\phi_{[c,\infty)}(x;\theta_{n},\sigma_{n})$
is $\Phi(-\frac{n+c}{n^{1/2}})^{-1}\phi(x;-n-c,n^{1/2})1_{x>c}$.
The normal density part equals 
\[
(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp\left(\frac{-n^{2}-2n(c+x)+[2cx-c^{2}-x^{2}]}{2n}\right)
\]
When $n$ is large compared to $x$ and $c$, $[2cx-c^{2}-x^{2}]/2n$
is negligible, hence 
\[
\phi(x;\theta_{n},\sigma_{n})\approx(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp(-n/2)\exp(-x-c)
\]
which equals $\exp(-x-c)\phi(n^{1/2})/n^{1/2}$.
Since $\Phi(-(\theta_{n}+c)/\sigma_{n})=\Phi(n^{1/2})\approx n^{1/2}/\phi(n^{1/2})$
as $n$ grows \citep[equation 5]{borjesson1979simple},
we end up with $$\Phi(-(\theta_{n}+c)/\sigma_{n})^{-1}\phi(x;\theta_{n},\sigma_{n})1_{x>c}\to\exp(-x-c)$$
\end{proof}
%
This lemma gives a mixture representation of the publication bias
model. The proof is omitted.
\begin{lem}
\label{prop:Mixture representation} The density of an observation
from the step function publication bias model with parameters $\theta_{0},\tau,\sigma_{i}$
is
\begin{equation}
f(x\mid\theta_{0},\tau,\sigma_{i})=\sum_{j=1}^{N}\pi_{j}\phi_{[\Phi^{-1}(1-\alpha_{j}),\Phi^{-1}(1-\alpha_{j-1}))}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})\label{eq:Random effects publication bias}
\end{equation}
where 
\[
\pi_{j}(\theta,\tau,\sigma_{i})=\rho_{j}\frac{\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})}{\sum_{j=1}^{J}\rho_{j}[\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]}.
\]
\end{lem}

>>>>

%% LyX 2.3.4.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\usepackage[natbibapa]{apacite}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{definition}
\newtheorem{example}[thm]{\protect\examplename}
\theoremstyle{plain}
\newtheorem{lem}[thm]{\protect\lemmaname}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{infiniteci}

@@

\renewcommand{\sqrt}[1]{{(#1)^{1/2}}}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\argmin}{argmin}
\DeclareMathOperator{\Cor}{Cor}
\DeclareMathOperator{\Cov}{Cov}
\DeclareMathOperator{\diag}{diag} 
\DeclareMathOperator{\argmax}{argmax}
\DeclareMathOperator{\supp}{supp}

\usepackage{enumitem}
\setlist[enumerate]{label = (\roman*)}

\makeatother

\usepackage{babel}
\providecommand{\definitionname}{Definition}
\providecommand{\examplename}{Example}
\providecommand{\lemmaname}{Lemma}
\providecommand{\theoremname}{Theorem}

\begin{document}
\title{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
\author{Jonas Moss \orcid{0000-0002-6876-6964}\\
Department of Mathematics, University of Oslo\\
PB 1053, Blindern, NO-0316, Oslo, Norway\emph{}\\
\emph{jonasmgj@math.uio.no}}
\maketitle
\begin{abstract}
Meta-analysis, the statistical analysis of results from separate studies,
is a fundamental building block of science. But the assumptions of
classical meta-analysis models are not satisfied whenever publication
bias is present, which causes inconsistent parameter estimates. Hedges'
selection function model takes publication bias into account, but
estimating and infering with this model is tough. Using a generalized
Gleser--Hwang theorem, we show there is no confidence set of guaranteed
finite diameter for the parameters of Hedges' selection model. This
result provides a partial explanation for why inference with Hedges'
selection model is fraught with difficulties.
\end{abstract}
\keywords{meta-analysis \and confidence intervals \and file-drawer  problem \and publication bias \and selection models \and weigth function models}

@@

A meta-analysis is a statistical analysis that quantiatively combines
results from separate scientific studies. When the studies measure
the same phenomenon, pooling of information allows us to predict the
common effect size with larger precision than we could have done with
one study alone. Meta-analyses are ubiquitous in the empirical sciences
and forms a key component of most systematic reviews such as Cochrane's
reviews \citep{Higgins2019-vv}.

Most meta-analytic techniques assume honest and unbiased reporting
of results. But there is ample evidence that the scientific literature
is not unbiased, as studies with\emph{ }significant \emph{p}-values
tend to be published with a greater probability than other studies
\citep{Easterbrook1991-ph}, a phenomenon called publication bias
by \citet{sterling1959publication} and the file-drawer problem by
\citet{Rosenthal1979-pm}. When publication bias is present, there
is no reason to trust the results of meta-analytic methods that do
not account for it, as the parameter estimates will be incosistent
\citep{Carter2019-rw}.

Hedges' \citeyearpar{hedges1992modeling} publication bias model takes
publication bias explicitly into account using a selection model,
and is arguably the most appropriate model for publication bias \citep{Carter2019-rw}.
Despite there being an $\mathtt{R}$ \citep{Team2013-tt} package
for maximum likelihood estimation of this model, called $\texttt{weightr}$
\citep{Coburn2019-ec}, the model has not yet taken off. Its maximum
likelihood estimation methods are numerically unstable and its estimates
can be off even when they converge \citep{Coburn2019-ec,Stanley2005-ng}.
The estimate of the mean effect size may be negative and of unrealistically
large magnitude, and the estimated heterogeneity parameter might be
improbably large. It turns out there are ridges in the likelihood
function that can be linked to this behavior \citep{McShane2016-rb},
but it has not been stated in clear terms exactly what the consequences
are for inferential procedures. The purpose of this note is to show
there is no confidence set for the mean effect size that has infinite
diameter with probability $0$. In the terminology of \citet{berger1999integrated},
Hedges' publication bias model belongs to the \emph{Gleser--Hwang}
class.

\section{Hedges' publication bias model}

The most popular and well-known meta-analysis method is the random
effects model with normal likelihoods \citep{hedges1998fixed}. Written
in hierarchical notation, it equals
\begin{eqnarray*}
\theta_{i} & \sim & N(\theta_{0},\tau),\\
x_{i}\mid\theta_{i},\sigma & \sim & N(\theta_{i},\sigma_{i}).
\end{eqnarray*}
Here $\sigma_{i}$ is the standard deviation of the $i$th study.
Following the convention in meta-analysis, we assume all $\sigma_{i}$s
to be known. The mean parameter $\theta$ is the population effect
size, $N(\theta_{0},\tau)$ is the effect size distribution, and $\tau$
is the heterogeneity parameter. The purpose of the effect size distribution
is to model the fact that most effect size estimates plugged into
a meta-analysis do not appear to measure the same phenomenon. By integrating
out $\theta_{i}$, we find the density of $x_{i}$,
\[
f(x_{i};\theta_{0},\tau,\sigma_{i})=\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}}),
\]
where $\phi$ is the density of a normal random variable.

We will assume that the random effects meta-analysis model is true
in the absence of publication bias. The mechanisms that cause publication
bias modify the density in a suitable way. Consider the case when
only significant studies at some specified level $\alpha$ are published.
Assuming one-sided tests, the \emph{p}-values are $u_{i}=\Phi(-x_{i}/\sigma_{i})$,
or normal one-sided \emph{p}-values. We will only deal with with one-sided
\emph{p}-values in this paper, as there is usually, but not always,
just one direction that is interesting to researchers, reviewers,
and editors. A one-sided \emph{p}-value can also be used if the researchers
reported a two-sided value, since $p=0.05$ for a two-sided hypothesis
corresponds to $p=0.025$ for a one-sided hypothesis, et cetera.

Define $c_{\alpha}=\Phi^{-1}(1-\alpha)$, the cutoff for significance
at level $\alpha$. The \emph{basic publication bias model} is a truncated
normal model with density
\begin{equation}
f(x_{i};\theta_{0},\sigma_{i})=\Phi\left(\frac{\theta_{0}-c_{\alpha}}{\sqrt{\sigma_{i}^{2}+\tau^{2}}}\right)^{-1}\phi(x;\theta_{0},\sqrt{\sigma_{i}^{2}+\tau^{2}})1[x_{i}/\sigma_{i}>c_{\alpha}],\label{eq:selection for significance model}
\end{equation}
This model for publication bias was introduced by \citet{hedges1984estimation}
in the context of $F$-distributions.

The basic publication bias model is unrealistic. It requires that
no non-significant studies are published. But even in the fields most
severely affected by publication bias, such as psychology, a non-negligble
number of non-significant studies are published \citep{Motyl2017-dx}.
Moreover, the basic publication bias model does not allow for different
cutoffs for significance. For instance, it is likely that some editors
will accept studies reaching a significance at $\alpha=0.025$, corresponding
to $x_{i}/\sigma_{i}>1.96$ but not at $\alpha=0.05$, corresponding
to $x_{i}/\sigma_{i}>1.64$.

These problems can be rectified by adopting the selection model for
publication bias of \citet{iyengar1988selection}, which models the
following scenario.
\begin{quote}
\textbf{Publication bias scenario.} Alice the editor receives a study
with the \emph{p}-value $u$. Her publication decision is a random
function of this \emph{p}-value. That is, she will publish the study
with some probability $w(u)$ and reject it with probability $1-w(u)$.
Every study you will ever read in Alice's journal has survived this
selection mechanism, the rest are lost forever.
\end{quote}
Let $w(u_{i})$ be a function of the \emph{p}-value $u_{i}=1-\Phi(-x_{i}/\sigma_{i})$
taking values in $[0,1]$. Then $w(u_{i})$ is a probability for every
$u_{i}$, and the selection model

\begin{equation}
f(x_{i};\theta_{0},\sqrt{\sigma_{i}^{2}+\tau^{2}})\propto\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})w(u)\label{eq:iyengar-greenhouse model}
\end{equation}
models the publication bias scenario exactly. This model can be viewed
as a rejection sampling procedure \citep{flury1990acceptance,von1951various},
where $\phi$ serves as proposal distribution for $f$. Variants of
this model, with and without covariates, has been studied by e.g.
\citet{Dear1992-gw,Vevea1995-on,Vevea2005-xp,citkowicz2017parsimonious}.

\citet{hedges1992modeling} studies the selection model when $w$
is a step function with fixed steps. Let $\alpha$ be a vector with
elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$
be a $K$-ary non-negative, non-increasing vector having its first
element equal to $\rho_{1}=1$. Define the step function $w$ based
on $\alpha$ and $\rho$ as
\begin{equation}
w(u;\rho,\alpha)=\sum_{k=1}^{K}\rho_{k}1_{(\alpha_{k-1},\alpha_{k}]}(u).\label{eq:step function}
\end{equation}
We call the selection model with a step function \emph{Hedges' publication
bias model. }Its density is
\begin{equation}
f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})\propto\sum_{k=1}^{K}\rho_{k}\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})1_{(\alpha_{k-1},\alpha_{k}]}(u_{i}).\label{eq:hedges model}
\end{equation}
Interpretating Hedges' publication bias model is easy. When the editor
receives a study with \emph{p}-value $u$, she finds the $j$ such
that $u\in(\alpha_{j-1},\alpha_{j}]$ and accepts with probability
$\rho_{j}$. Since $\rho_{1}=1$, she always accepts when $u\in[0,\alpha_{1}]$.
The vector $\rho$ is non-increasing since a publication decision
based solely on \emph{p}-values should always act favorably towards
lower \emph{p}-values. The parameters $(\theta_{0},\tau,\rho)$ of
the model are identified when $\alpha$ is fixed \citep[Web Appendix A]{moss2019modelling}.

Hedges' publication bias models allows both for non-significant studies
to be published and allows the editor to act differently towards different
cutoffs such as $\alpha=0.025$ and $\alpha=0.05$. In addition, the
model can approximate any non-increasing selection function $w$ by
increasing the number of steps.

We can write Hedges' model as a mixture model on the form
\begin{equation}
f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})=\sum_{k=1}^{K}\pi^{k}f^{k}(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}}).\label{eq:mixture model formulation}
\end{equation}
Here $f^{K}$ is a normal density, $f^{k},k<K$ are normal densities
truncated to $[\Phi^{-1}(1-\alpha_{j-1}),\Phi^{-1}(1-\alpha))$, and
$\pi^{k}$ are mixture probabilities, i.e., $\pi^{k}>0$ for each
$k$ and $\sum_{k=1}^{K}\pi^{k}=1$. The mixture probabilities $\pi^{k}$
are functions of $(\theta_{0},\tau,\sigma_{i},\rho)$, see the appendix
(p. \pageref{eq:pi_i formula}) for their formula.

The main benefit of Hedges' publication bias model (\ref{eq:hedges model})
is how it models \emph{p}-values based publication bias directly,
there is no approximation involved. If you believe in the random effects
meta-analysis model and the \emph{p}-value based publication bias
scenario, Hedges' publication bias model is simply the correct model.
Most statistical methods correcting for publication bias in the literature
either do not make use of an explicit statistical model or do not
estimate the parameters $\theta_{0}$ and $\tau$. For instance, the
funnel funnel plot of \citet{Egger1997-rd} is a graphical method,
while the trim-and-fill method of \citet{Duval2000-ct} is a non-parametric
method based on making the funnel plot symmetric. \citet{Stanley2005-ng,stanley2014meta}
discuss various misspecified regression-based estimators of the corrected
effect size $\theta$ based on the fixed effect Hedges' publication
bias model. The estimating \emph{p}-curve method of \citet{Simonsohn2014-cn}
and \emph{p}-uniform of \citet{Van_Assen2015-qs,Van_Aert2016-cu}
are two methods for dealing with publication bias hailing from psychology.
Both are based on a variant of the basic publication bias model, but
with fixed instead of random effects, and both employ somewhat unusual
estimation methods \citep{McShane2016-rb}. Since there is ample evidence
of heterogeneity in meta-analysis, restricting oneself to the fixed
effects meta-analysis is a mistake.

Hedges' model has some downsides. It models only bias due to selection
of \emph{p}-values, not every source of bias, such as language bias
\citep{Egger1998-kj}. Second, it may not be best model for biases
with other causes than the publication process, such as \emph{p}-hacking
\citep{simmons2011false}. \citet{moss2019modelling} propose a related
model that may be more successful at correcting for \emph{p}-hacking.

Estimation of Hedges' model is difficult. \citet[Section 6.3]{Stanley2005-ng}
discusses three problematic cases in economics when maximum likelihood
was used to estimate Hedges' publication bias model. \citet[Appendix A]{McShane2016-rb}
notes that while estimation of the basic publication bias model is
hard, introducing the heterogeneity parameter exacerbates the problem.
The likelihood function has contours following approximately $\tau\propto\sqrt{|\theta|}$.
Figure \ref{fig:contour lines} shows the contour lines for the meta-analysis
of \citet{Cuddy2018-kp} where the selection probabilities of the
step function (\ref{eq:step function}) are fixed at $\rho=(1,0.6,0.1)$.
Only just around the maximum at $\hat{\theta}_{0}=0.55$ and $\hat{\sigma}=5\cdot10^{-7}$
can the likelihood be approximated with a quadratic function.

\begin{figure}
\noindent \begin{centering}
\includegraphics[scale=0.5]{chunks/cuddy}
\par\end{centering}
\caption{\label{fig:contour lines}Contour lines for the log-likelihood for
the simple publication model using power posing data of \citet{Cuddy2018-kp}. }

\end{figure}

\section{Confidence sets of infinite diameter}

Fix some measurable space $(\Omega,\mathcal{F})$, let $\mathcal{P}$
be a family of dominated probability measures defined on this measurable
space, and $\mathcal{\Pi}$ a partition of $\mathcal{P}$. Recall
that a partition of $\mathcal{P}$ is a collection of disjoint non-empty
subsets $\pi$ of $\mathcal{P}$ such that $\bigcup_{\pi\in\Pi}\pi=\mathcal{P}$.
When $p$ is a density associated with a $P\in\mathcal{P}$, we will
use the standard notation $[p]$ to denote the unique $\pi$ containing
$P$. 
\begin{defn}
\label{def:confidence set} A \emph{confidence set} of level $\alpha$
is a family of rejection sets $\{R(\pi)\},\pi\in\Pi$ such that
\[
\sup_{\pi\in\Pi}\sup_{P\in\pi}P(R(\pi))\leq\alpha.
\]
If the inequality is an equality, the confidence set has \emph{size}
$\alpha$. 
\end{defn}

This definition of confidence sets might look slightly unfamiliar,
but it is a straight-forward generalization of the definitions in
\citet[Definition 9.1.5]{Casella2002-lg} and \citet[Section 3.5]{lehmann2006testing}.
Usually, a confidence is defined as a set $C$ adhering to the relation
\begin{equation}
\pi_{0}\in C\iff\omega\notin R(\pi_{0}).\label{eq:c-confidence set}
\end{equation}
That is, $\pi_{0}\in C$ if and only if we accept the null-hypothesis
$H_{0}:\pi=\pi_{0}$, but will only need the formulation using rejection
sets in this paper. When confidence sets are defined in terms of rejection
sets, there is sometimes no partition $\Pi$ to take the supremum
over, and the definition reduces to $\sup_{P\in\mathcal{P}}P(R(P))\leq\alpha$.
The term\emph{ confidence interval} is far more common than confidence
set, but this requires that $C$ of equation \ref{eq:c-confidence set}
is an interval, which we will not require here.

The following example should make Definition \ref{def:confidence set}
familiar.
\begin{example}
\label{exa:t-test} Consider the usual \emph{t}-confidence interval
with $n$ observations. Here $\mathcal{P}$ contains all measures
$P_{\mu,\sigma}^{n}$, where $P_{\mu,\sigma}$ is the probability
measure of a normal with mean $\mu$ and standard deviation $\sigma$.
Furthermore, when $Q$ is a probability measure, $Q^{n}$ denotes
the $n$-fold product measure of $Q$, corresponding to $n$ independent
samples from $Q$. Let $\pi(\mu)=\{P_{\mu,\sigma}^{n}\mid\sigma>0\}$
contain all normal probability measures with mean $\mu$ and some
positive standard deviation. Then $\{\pi(\mu)\},\mu\in\mathbb{R}$
defines a partition of $\mathcal{P}$. A two-sided \emph{t}-confidence
interval is a confidence set of size $\alpha$ with partition $\{\pi(\mu)\},\mu\in\mathbb{R}$
according to definition \ref{def:confidence set}.
\end{example}

Now we must find out how to measure the size of confidence sets. Let
a \emph{size function} be any positive function $\left\Vert \cdot\right\Vert :\Pi\to[0,\infty)$.
In the \emph{t}-confidence interval example above, $\left\Vert \cdot\right\Vert $
can be taken to be $\left\Vert \pi\right\Vert =|\mu|$ for the unique
$\mu$ associated with each $\pi$.
